Tor's Usability for Censorship Circumvention

### 2016-04-04 pets2017-paper/pets2017-paper.tex
finish qualitative results proxy subsubsubsubsection.

\noindent {\bfseries Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error.

@@

\noindent {\bfseries Proxy Configuration} 
%proxies
\begin{quotation}
\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\

\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
\end{quotation}

If users did not successfully connect on their first attempt, they did not know what to do next. Error messages did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.). Because no information was given, our participants drew their own (incorrect) conclusions after a failed connection. Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.\\

>>>>

\noindent {\bfseries Bridge Configuration} 
When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary. Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen. We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error. Most participants with the default option to not configure a bridge.

@@

\noindent {\bfseries Proxy Configuration} 
After the bridge configuration, the participant again is asked to answer a question to determine if they need a proxy and if so, to configure one. This question also was too technical for some participants.

\begin{quotation}
\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''}
\end{quotation}

None of our censorship environments required our participants to configure a proxy for a successful connection. And upon the first attempt at configuration, most chose the default value of not configuring a proxy.  However, the most common reason for of failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead. Currently, no information was given upon failing to connect, which caused our participants to draw their own (incorrect) conclusions after a failed connection. Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.

None of the participants who attempted to configure a proxy were successful. Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information. What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.

%proxies
\begin{quotation}
\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
\end{quotation}

Providing participants with feedback about taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc. can prevent participants from unnecessarily configuring a proxy and to connect successfully. \\
